Predicting the 2024 U.S. Presidential Election: Trump’s Likely Victory Based on Polling Analysis

### 2024-11-03 paper/paper.qmd
committing text changes to paper.qmd

@@

- $ \text{Trump\_pct}_i $ and $ \text{Harris\_pct}_i $ are the polling support levels for Donald Trump and Kamala Harris in state $ i $.
- $ f(\text{end\_date\_num}_i) $ is a natural spline function of time (measured as $ \text{end\_date\_num} $), with 4 degrees of freedom, capturing the non-linear time trends in support.
- $ \alpha_{\text{Trump}} $ and $ \alpha_{\text{Harris}} $ are intercepts for the models, representing the baseline support levels for each candidate.
- $ u_{\text{state}}^{\text{Trump}} $ and $ u_{\text{state}}^{\text{Harris}} $ are state-level random effects, accounting for differences in baseline support across states.

>>>>

## Other Variables

@@

- \begin{equation}
  \text{Trump\_pct}_i \text{ and } \text{Harris\_pct}_i \text{ are the polling support levels for Donald Trump and Kamala Harris in state } i.
  \end{equation}

- \begin{equation}
  f(\text{end\_date\_num}_i) \text{ is a natural spline function of time (measured as } \text{end\_date\_num}, \text{ with 4 degrees of freedom, capturing the non-linear time trends in support.}
  \end{equation}

- \begin{equation}
  \alpha_{\text{Trump}} \text{ and } \alpha_{\text{Harris}} \text{ are intercepts for the models, representing the baseline support levels for each candidate.}
  \end{equation}

- \begin{equation}
  u_{\text{state}}^{\text{Trump}} \text{ and } u_{\text{state}}^{\text{Harris}} \text{ are state-level random effects, accounting for differences in baseline support across states.}
  \end{equation}
